\ttitle

### 2015-06-02 Chapters/Introduction.tex
complete first paragraph of jaundice introduction

>>>>

Until recently, major surgery in the jaundiced patient has been considered to be more prone to adverse postoperative events. While this concept has been recently challenged, surgeons remain wary of the severely jaundiced patient.

Pancreaticoduodenectomy was initially described as a two-stage procedure where the first stage involved a biliary bypass aimed at relieving obstructive jaundice before the second stage of resection was carried out.
